Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits

### 2018-12-03 Manuscript_draft/Manuscript_draft.Rmd
Advances

**Paragraph 1**

@@

**Paragraph 2**

Recent studies have advanced in the ecological understanding of heterospecific pollen effect @morales2008 @ashman2013 @arceo2016. A general overview of foreign pollen arrival is that it can play an important role on species fitness but seems to be context dependent and not always produce a decrease in fitness @morales2008. Part of this unpredictability is due to the enormous variability of foreing pollen transferred in nature, where levels between 0 and 75 percent are seen, but most commonly values ranges between 10 and 20 percent of the total pollen load, being the generalist species the ones that receive greater loads of heterospecific pollen @montgomery2012 @fang2013. Although heterospecific pollen quantity is fundamental to understand the outcome of the interaction so is the different traits of both pollen donor and recipient. @ashman2013 postulated the first predictive framework for traits of heterospecific pollen effect where traits such as compatibility system and pollen size among others should be crucial to understand foreing pollen effect. Moreover, in @tong2016 a assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the ful length of the style on short styled species but not viceversa. Despite these recent caveats, we still lack empirical evidence to affirm what are the main traits that drive heterospecific pollen effect for both pollen donor and recipient at seed production level. Interestingly, this trait based question of effect between a pair of species cannot be solved without consider the phylogenetic relatedness of them. A general view is that close related species will have greater negative impact than far related species (REFS). Muchas especies inclusos congeneres difieren en traits

Plenty of work have consider crosses between close related species, showing both negative and none effect. One of the concerns at seed set level is that in case that species are able to hybridised the negative impact of heterospecific pollen effect is hidden.

**Paragraph 3**

@@

Few studies have tried to understand how relatedness is involved in the hp effect but generally

Until our knowledge ....

@@

**Paragraph 3**

@@

**Paragraph 4**

>>>>

**Paragraph 1** General idea to our concept

@@

**Paragraph 2** Introducing topic and knowledge gap

Recent studies have advanced in the ecological understanding of heterospecific pollen effect @morales2008 @ashman2013 @arceo2016. A general overview of foreign pollen arrival is that it can play an important role on species fitness but seems to be context dependent and not always produce a decrease in fitness @morales2008. Part of this unpredictability is due to the enormous variability of foreing pollen transferred in nature, where levels between 0 and 75 percent are seen, but most commonly values ranges between 10 and 20 percent of the total pollen load, being the generalist species the ones that receive greater loads of heterospecific pollen @montgomery2012 @fang2013. Although heterospecific pollen quantity is fundamental to understand the outcome of the interaction so is the different traits of both pollen donor and recipient. @ashman2013 postulated the first predictive framework for traits of heterospecific pollen effect where traits such as compatibility system and pollen size among others should be crucial to understand foreing pollen effect. Moreover, in @tong2016 a assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the ful length of the style on short styled species but not viceversa. Despite these recent caveats, we still lack empirical evidence to affirm what are the main traits that drive heterospecific pollen effect for both pollen donor and recipient at seed production level. Interestingly, this trait based question of effect between a pair of species cannot be solved without consider the phylogenetic relatedness of them. A general view is that close related species will have greater negative impact than far related species (REFS) but few studies test this fact. The interaction between close related species have been tradionally overlooked (Refs) but not always the effect of congeners or confamilias can be seen due to these other species are capable of fertilization (Refs.) Combining both traits and phylogenetic relatedness could give a better picture of how both parts interact in the heterospecific pollen process.

**Paragraph 3** Expanding ideas with examples

Examples of articles...

@@

Few studies have tried to understand how relatedness is involved in the hp effect but generally 
Until our knowledge ....

@@

@@

**Paragraph 4** Introducing our experiment

### 2018-12-03 Manuscript_draft/Manuscript_draft.tex
Advances

\textbf{Paragraph 1}

@@

\textbf{Paragraph 2}

Recent studies have advanced in the ecological importance of
heterospecific pollen effect Morales and Traveset (2008) Ashman and
Arceo-Gómez (2013) Arceo-Gómez and Ashman (2016). A general overview of
foreign pollen arrival is that it can play an important role on species
fitness but seems to be context dependent and not always produce a
decrease in fitness Morales and Traveset (2008). Part of this
unpredictability is due to the enormous variability of foreing pollen
transferred in nature, where levels between 0 and 75 percent are seen,
but most commonly values ranges between 10 and 20 percent of the total
pollen load, being the generalist species the ones that receive greater
loads of heterospecific pollen Montgomery and Rathcke (2012) Fang and
Huang (2013). Although heterospecific pollen quantity is fundamental to
understand the outcome of the interaction so is the different traits of
both pollen donor and recipient. Ashman and Arceo-Gómez (2013)
postulated the first predictive framework for traits of heterospecific
pollen effect where traits such as compatibility system and pollen size
among others should be crucial to understand foreing pollen effect.
Moreover, in Tong and Huang (2016) a assymetric effect was shown in a
crossing experiment between 6 species of the genus \emph{Pedicularis}
where the pollen of long styled species was able to grow the ful length
of the syle on short styled species but not viceversa. Despite these
recent caveats, we still lack empirical evidence to affirm what are the
main traits that drive heterospecific pollen effect for both pollen
donor and recipient at seed production level. Interestingly, this trait
based question cannot be solved without consider the phylogenetic
relatedness of the species. A commonly understanding is that close
related species will have greater negative impact

\textbf{Paragraph 3}

@@

Few studies have tried to understand how relatedness is involved in the
hp effect but generally

Until our knowledge \ldots{}.

@@

\textbf{Paragraph 3}

@@

\textbf{Paragraph 4}

>>>>

\textbf{Paragraph 1} General idea to our concept

@@

\textbf{Paragraph 2} Introducing topic and knowledge gap

Recent studies have advanced in the ecological understanding of
heterospecific pollen effect Morales and Traveset (2008) Ashman and
Arceo-Gómez (2013) Arceo-Gómez and Ashman (2016). A general overview of
foreign pollen arrival is that it can play an important role on species
fitness but seems to be context dependent and not always produce a
decrease in fitness Morales and Traveset (2008). Part of this
unpredictability is due to the enormous variability of foreing pollen
transferred in nature, where levels between 0 and 75 percent are seen,
but most commonly values ranges between 10 and 20 percent of the total
pollen load, being the generalist species the ones that receive greater
loads of heterospecific pollen Montgomery and Rathcke (2012) Fang and
Huang (2013). Although heterospecific pollen quantity is fundamental to
understand the outcome of the interaction so is the different traits of
both pollen donor and recipient. Ashman and Arceo-Gómez (2013)
postulated the first predictive framework for traits of heterospecific
pollen effect where traits such as compatibility system and pollen size
among others should be crucial to understand foreing pollen effect.
Moreover, in Tong and Huang (2016) a assymetric effect was shown in a
crossing experiment between 6 species of the genus \emph{Pedicularis}
where the pollen of long styled species was able to grow the ful length
of the style on short styled species but not viceversa. Despite these
recent caveats, we still lack empirical evidence to affirm what are the
main traits that drive heterospecific pollen effect for both pollen
donor and recipient at seed production level. Interestingly, this trait
based question of effect between a pair of species cannot be solved
without consider the phylogenetic relatedness of them. A general view is
that close related species will have greater negative impact than far
related species (REFS) but few studies test this fact. The interaction
between close related species have been tradionally overlooked (Refs)
but not always the effect of congeners or confamilias can be seen due to
these other species are capable of fertilization (Refs.) Combining both
traits and phylogenetic relatedness could give a better picture of how
both parts interact in the heterospecific pollen process.

\textbf{Paragraph 3} Expanding ideas with examples

Examples of articles\ldots{}

@@

Few studies have tried to understand how relatedness is involved in the
hp effect but generally Until our knowledge \ldots{}.

@@

@@

\textbf{Paragraph 4} Introducing our experiment
